A Container-Based Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-10-14 draft.tex
Update draft.tex

We organized the paper as follows: First, in Section \ref{multi}, we present a
background of the fundamental issues of integrating nature-inspired optimization
and multi-population methods. Section \ref{soa} presents state of the art relevant to
our work. In Section \ref{method}, we present the proposed method and the container-based
application in Section \ref{docker} and the workflow for reproducible experiment design in Section \ref{experiment_flow}. % No reference to section 6.
Section \ref{setup} describes the design of the empirical evaluation to assess the effectiveness
of the method,  with respect to scalability and % This is a subsection, fix it. 
the heterogeneous populations' performance.  % No references to sections 9 and 10
Finally, we offer the conclusions of this paper and suggestions on future work in Section \ref{conclusions}.

>>>>

We organized the paper as follows: First, in Section \ref{multi}, we present a
background of the fundamental issues of integrating nature-inspired optimization
and multi-population methods. Section \ref{soa} presents state of the art relevant to
our work. In Section \ref{method}, we present the proposed method and the container-based
application in Section \ref{docker} and the workflow for reproducible experiment design in Section \ref{experiment_flow}. % No reference to section 6.
Section \ref{setup} describes the empirical evaluation design to assess the effectiveness
of the method, concerning scalability and % This is a subsection, fix it. 
the heterogeneous populations' performance.  % No references to sections 9 and 10
Finally, we offer the conclusions of this paper and suggestions for future work in Section \ref{conclusions}.
